Verifying Concurrent Search Structure Templates for C Programs using VST

### 2023-04-23 concurrency/CONCUR 2023/paper.tex
fix breakage and restructured
fix some breakage

\subsection{Iris and VST}

@@

In contrast to the lock-coupling style, where each lock is associated with a lock-invariant—an arbitrary separation logic predicate representing the protected resource acquired by a thread when the lock is obtained and must be restored upon lock release—the give-up template has a different approach. In this method, every node possesses a lock bit at location $\ell$, which is set to \texttt{True} if and only if the node is locked. This protocol is encoded into the definition of the abstract state $\treerep$. The lock protects resources denoted by \texttt{R}, which can be removed from $\treerep$ by threads when the node is locked.

@@

\than{Or can we move this section to Proof mechanization, where we talk on BST speficially.}

@@

@@

\subsection{Lock-coupling Template}
\begin{figure}[ht]
	\begin{subfigure}[t]{0.48\textwidth}
	\lstinputlisting[language=C, style=myStyle, escapechar=|]{lock_insert.c} 
	\caption{The \lstinline{insert} method of the lock-coupling template algorithm}
	\label{insert_lock}	
	\end{subfigure}\qquad
    \begin{subfigure}[t]{0.48\textwidth}
    \lstinputlisting[language=C, style=myStyle]{giveup_insert.c} 
    \caption{The \lstinline{insert} method of the give-up template algorithm}
    \label{insert_giveup}
    \end{subfigure} 
\caption{The \lstinline{insert} method of the lock-coupling and give-up template algorithms}
\label{insert_lock_giveup} 
\end{figure}

@@

The \texttt{inRange} specification (Figure \ref{fig:inRange_insertOp_giveup}) simply necessitates that \texttt{inRange(pn, k)}  yields a boolean value, \texttt{res}. When \texttt{res} is \texttt{True}, it signifies that \texttt{k} is within the range of \texttt{(min, max)} associated with the node \texttt{n}. 
Conversely, \texttt{res} is \texttt{False}, it indicates that \texttt{k} is outside the boundaries of \texttt{(min, max)}.

@@

>>>>

\subsection{Iris and VST}
\than{write more here ... }

@@

In contrast to the lock-coupling style, where each lock is associated with a lock-invariant—an arbitrary separation logic predicate representing the protected resource acquired by a thread when the lock is obtained and must be restored upon lock release—the give-up template has a different approach. In this method, every node possesses a lock bit at location $\ell$, which is set to \texttt{true} if and only if the node is locked. This protocol is encoded into the definition of the abstract state $\treerep$. The protocol is formally defined as $\texttt{inv\_for\_lock} \ \ell \ \texttt{R} \triangleq \exists b. \ \ell \mapsto b \ \ast \ \texttt{if } b \ \texttt{then emp else R}$, where a lock at location $\ell$ safeguards resources denoted by \texttt{R}. When the lock is held, meaning the node is locked ($\ell \mapsto \texttt{true}$), threads can remove resources \texttt{R} from $\treerep$. On the other hand, when the lock is not held ($\ell \mapsto \texttt{false}$), resources \texttt{R} are required to be part of the invariant.

@@

@@

\than{Write more here ... }

@@

\subsection{Lock-coupling Template}
\begin{figure}[h]
	\begin{subfigure}[t]{0.48\textwidth}
	\lstinputlisting[language=C, style=myStyle, escapechar=|]{lock_insert.c} 
	\caption{The \lstinline{insert} method of the lock-coupling template algorithm}
	\label{insert_lock}	
	\end{subfigure}\qquad
    \begin{subfigure}[t]{0.48\textwidth}
    \lstinputlisting[language=C, style=myStyle]{giveup_insert.c} 
    \caption{The \lstinline{insert} method of the give-up template algorithm}
    \label{insert_giveup}
    \end{subfigure} 
\caption{The \lstinline{insert} method of the lock-coupling and give-up template algorithms}
\label{insert_lock_giveup} 
\end{figure}

@@

The \texttt{inRange} specification (Figure \ref{fig:inRange_insertOp_giveup}) simply necessitates that \texttt{inRange(pn, k)}  yields a boolean value, \texttt{res}. When \texttt{res} is \texttt{true}, it signifies that \texttt{k} is within the range of \texttt{(min, max)} associated with the node \texttt{n}. 
Conversely, \texttt{res} is \texttt{false}, it indicates that \texttt{k} is outside the boundaries of \texttt{(min, max)}.

@@

\than{Write more ...}
